---
title: "Fitting Models *Without* parsnip"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Fitting Models *Without* parsnip}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, message=F}
library(tidymodels)
library(broom.mixed)
library(tyecon)
data(ames)
```

# Fitting Models Without parsnip

This vignette shows how we can achieve the same (if not better) consistency of using multiple models together without the need for packages such as `parsnip` or `broom`. Original article which uses these two packages can be found in the tidymodels book, [here](https://www.tmwr.org/models.html).

## The linear functions family

To build this family, we simply encapsulate the three `lm`, `stan_glm`, and `glmnet` functions together, using `tyecon::convoke`:

```{r, message=F}
library(rstanarm)
library(glmnet)
```

```{r}
ames_split <- initial_split(ames, prop = 0.80)
ames_train <- training(ames_split)
```

First, we unify the models: 

```{r, message=F}
(linear_model <-
    convoke(list(formula, data),
            lm(formula = formula, data = data) ~ .,
            stan_glm(formula = formula, data = data, mean_PPD = FALSE) ~ .,
            glmnet(x = model.frame(formula, data = data)[-1],
                   y = model.frame(formula, data = data)[[1]]) ~ .))
```

```{r, results='hide'}
model_results <- enframe(map(set_names(names(linear_model)), ~
    linear_model(Sale_Price ~ Longitude + Latitude, ames_train, interface = .)),
    "modelname", "model") %>% rowwise
```

```{r}
(model_results <- mutate(model_results, vcov_val =
                         list(possibly(vcov, NULL)(model))))
```

Now we'd want to see the coefficients, possibly alongside some other information. In fact, we may want to know a lot more about each model as well.

```{r}
(model_results <- mutate(model_results, coef_val =
                         list(possibly(coef, NULL)(model))))
```

We can also store the tidy variant:

```{r}
(model_results <- mutate(model_results, tidy_val =
                         list(possibly(tidy, NULL)(model))))
```

We can also plot the results rather easily. First, let us make a unified plot function using `conflate`, as `plot` is simply a generic function:

```{r}
(conflated_plot <- conflate(plot(x)))
```


```{r, eval=F}
par(mfrow=c(2,2))
walk(pull(model_results, model), ~
    conflated_plot(., lm.ask = FALSE, lm.which = 1,
                   elnet.xvar = "dev", stanreg.plotfun = "hist"))
```

