---
title: "Example Issues"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Example Issues}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include = FALSE}
rm(list = ls())
library(tyecon)
library(rlang)
library(purrr)
library(stringr)
library(tibble)
```

# The `convoke` Function

Here is one example of different function interfaces doing the same thing and how the provided DSL would simplify this issue.

The two functions each take a different data type in, produce a different out data, use different name for trim argument, and one does not have a default value for column (works only on vectors).

```{r example-funcs}
basemeancalc <- function(listdata, trimmed = 0.0, na.rm = T){
    mean(listdata, trim = trimmed, na.rm = na.rm)
}

tidymeancalc <- function(tibbledata, column, trimend = 0.0, trimstart = 0.0){
    column <- as_string(ensym(column))
    colvector <- tibbledata[[column]] %>% sort %>% na.omit
    nelem <- length(colvector)
    colvector <- colvector[floor(nelem*trimstart) + 1 : nelem - floor(nelem*trimend)]
    return(mean(colvector))
}

mydf <- tribble(~x, ~y,
                1, 5,
                4, 3,
                6, 2,
                17, 4,
                8, 12,
                14, 16,
                21, 72,
                19, 32,
                10, 15,
                NA, NA)

tidymeancalc(mydf, x, trimend = 0.1, trimstart = 0.1)
basemeancalc(mydf$x, trimmed = 0.1)
mean(mydf$x, trim = 0.1, na.rm = T)
```

Three vastly different APIs. Now, for unification:

```{r convoke-example}
(mymean <- convoke(list(tibble, column, trim),
       basemeancalc(listdata = tibble[[column]], trimmed = trim) ~ .,
       tidymeancalc(tibbledata = tibble, column = !!column, trimend = trim,
                    trimstart = trim) ~ .))
```

```{r}
map(set_names(c("basemeancalc", "tidymeancalc")),
              ~ mymean(mydf, "x", 0.1, interface = ., basemeancalc.na.rm=T))
```

One can also add additional specifications later:

```{r}
mymean <- mymean + (mean(x = tibble[[column]], trimmed = trim) ~ .)
mymean(mydf, "x", 0.1, interface = "mean", mean.na.rm=T)
```

Nevertheless, the ultimate goal is to specify a DSL by which the package author can convert its functions to a unified interface by only specifying some general rules (in a text file bundled with the package for instance). This would allow the package author to separate the need to conform with a unified interface from writing the packages however is seen best.
Nevertheless, hard-codded values can't be changed or passed down obviously, and would still require upstream fixes.

# The `%to%` Operator

This operator facilitates a different issue that arises quite often in model building. And that is requiring multiple results from the same object. Example:

```{r}
modelfit <- lm(y ~ x, data = mydf)
(res <- summary(modelfit) %to% {
    rsquared ~ .$r.squared
    adjrsquared ~ .$adj.r.squared
    residuals ~ .$residuals
    pval ~ coef(.)[,"Pr(>|t|)"]
    termsof ~ .$terms
    callof ~ .$call
})
```

For instance, we can know the p-values now:

```{r}
res$pval
```

Comparing this with the result from `broom::glance`, one can see that the above approach is much more flexible.

